%!TEX root = ../paper.tex
This section discusses the previously presented results. We first consider the lack of difference in performance between the two estimators. The section after that is concerned with the anisotropy of the kernels used by the shape-adaptive estimator. Finally we offer some directions research into solving the identified issues might take.

\subsection{Performance}
\label{s:discussion:performance}
\input{discussion/performance}

\subsection{Kernel Anisotropy}
\label{s:discussion:anisotropy}
\input{discussion/anisotropy}

In closing we have found that near Gaussian components with a high volume eigensphere the kernels are too isotropic, whereas in the uniform random background fine structures are detected that result in too anisotropic kernels. Both of these problems might be solved by increasing the value of \KNNK. 
% Effect on noise:
We expect that increasing the size of the local neighborhood will decrease the number of detected fine structures. Which results in more isotropic kernels for points that lie in the uniform background.
% Effect on low density gaussians: 
Furthermore increasing \KNNK might also allow the kernels to adapt their shape to nearby Gaussian components whose eigensphere has a high volume. Multiplying the \KNNK computed in \cref{eq:method:k} by ten, resulted in \sambe outperforming \mbe on dataset \baakmanFive. Furthermore the increased \KNNK also improved the performance of \sambe on dataset \ferdosiThree, \baakmanThree and the datasets with a single Gaussian component. Whereas the performance of \sambe on dataset \ferdosiTwo and \baakmanTwo suffered. This shows that blindly increasing the size of the local neighborhood does not consistently improve the performance of the estimator, but that some adaptive increase of \KNNK is required.

Another solution to the too anisotropic kernels in the noise might be to only use shape-adaptive kernels if the neighborhood is sufficiently anisotropic. One might even consider using a kernel-shape that is somewhere between the isotropic and the fully anisotropic kernel depending on the anisotropy of the local neighborhood. A challenge with this approach is detecting the isotropy of the local neighborhood. Since the obvious solution, the covariance matrix, has proven sensitive to fine structures within the uniform random background.
%Alternative to the covariance matrix
One possible alternative to the covariance matrix is the Hessian matrix. A potential issue with this approach is that it uses second order derivatives. Firstly this may lead to it detecting more fine local structures in the background. Secondly the used Epanechnikov kernel would have to be replaced with a kernel that has second order differentiability.

Finally the correlation between the performance of the estimators and the volume of the eigensphere of the Gaussian component suggests that the method used to compute the local bandwidths is far from ideal. 
% Solution
One possible solution, at the cost of increased computational complexity, might be to use the method proposed by \citeauthor{breiman1977variable}.