%!TEX root = ../paper.tex

This section presents the results of the experiments described in \cref{s:experiment}. 
%MSE
We compare the performance of the two estimators on each data set with the \mse and visually with plots. Furthermore how well the shape of the kernels is adapted to the local neighborhood is investigated with their anisotropy.
% Plots
	% Axes
	All two-dimensional plots associated with a single data set have the same domain and range, to allow for easy comparison of the results within a data set. The horizontal axis is used to represent the known densities, its range is such that each known density can be shown. The estimated densities are shown on the vertical axis, we have ensured that the domain of these axes is such that they are long enough to represent every estimated density for that data set, independent of the used estimator. 
	% Perfect performance line
	The black line in the two-dimensional plots illustrates the line all points would lie on if a perfect estimator was used.
	% Colors
	The colors of the points in these plot correspond to the colors of the elements of the data sets in \cref{tab:experiment:singlesphere:sets,tab:experiment:multisphere:sets}.

% Structure of the section
	\Cref{s:results:singleGaussian} presents the results of the data sets that contain a single Gaussian, in \cref{s:results:multipleGaussian} the results of data sets that consist of noise and multiple Gaussian distributions are presented. 

\subsection{Data sets with a Single Gaussian}
\label{s:results:singleGaussian}
\input{result/singleSphere/main}

\subsection{Data sets with Multiple Gaussians}
\label{s:results:multipleGaussian}
\input{result/multiSphere/main}

%Some final general observation for all sets
	% Small differences in MSE between the two datasets
	In conclusion for all data sets we have only found very small differences in \mse between the two estimators. 
	% Both estimators perform better on denser gaussian components
	Furthermore both estimators perform better on points drawn from Gaussian components with a smaller eigensphere. 
	% Anisotropy is storngest on noise component
	Concerning the anisotropy of the kernels we have observed that in all data sets this statistic is highest for the noise component. 
	% Positve correlation between mean anisotropy of kernels and anisotropy of the gaussian comonent
	Comparing the means of the anisotropies of the kernels associated with the points drawn from the Gaussian components showed a positive correlation with the anisotropy of the component the point was sampled from. It should be noted that this relation has not been observed between the anisotropy of the Gaussian components in the data sets with a single Gaussian and the anisotropy of the kernels of points sampled from the uniform random background.